R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2025-03-08 main.tex
fix(action): rename main file

% We import package amsmath before the documentclass to avoid the warning.
% Command '\usepackage{amsmath}' results in the following warning:
% Package amsmath Warning: Unable to redefine math accent \vec.
\RequirePackage{amsmath} % for environments such as align

@@

% If possible, figure files should be included in EPS format.

% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\usepackage[export]{adjustbox} % for valign option in \includegraphics
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
% \usepackage{bbm} % for \mathbbm
\usepackage{dsfont}
\newcommand{\mathbbm}[1]{\mathds{#1}}
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{cleveref} % for \cref
\usepackage{csvsimple} % for \csvreader
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

% set the path for figures
\graphicspath{{./src/img}{./src/experiments}}

@@

% TODO REBUTTAL: Please enter paper ID
\def\paperID{735} % *** Enter the paper ID here

@@

% The authors' affiliations
\institute{Division of Computer Science and Information Technology\\
  Graduate School of Information Sci.\ and Tech.,
  Hokkaido University\\
  Sapporo 060--0814, JAPAN,\\
  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}

@@

\section{Introduction}
In recent years,
complex machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvements in accuracy.
However,
their increasing complexity and black-box nature pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the lack of transparency becomes a major obstacle to implementation.
In order to address this problem,
extensive research has focused on post-hoc explanations for complex models
~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
Post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
with the latter further classified into \emph{global} and \emph{local} methods
based on the locality in the input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \vspace{-2.24cm}
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

@@

\section{Proposed Method}
\begin{figure}[tbp]
  \centering
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-lime}
    \caption{%
      LIME\@: Locally approximates the decision boundary around the focal point.
    }\label{fig:lime}
  \end{subfigure}%
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-anchor}
    \caption{%
      Anchor: Maximizes coverage of a rectangular region
      containing the focal point under accuracy constraints.
    }\label{fig:anchor}
  \end{subfigure}
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{visual-rlime3}
    \caption{%
      R-LIME\@:
      Maximizes coverage of a rectangular region
      under lower constraints on the accuracy of the linear classifier.
    }\label{fig:rlime}
  \end{subfigure}
  \caption[Visual comparison of LIME, Anchor and R-LIME]{%
    Visual comparison of LIME, Anchor and R-LIME (our method).
    The dashed line represents the local linear approximation model,
    and the solid line represents the rectangular region containing the focal point.
  }
\end{figure}

@@

\subsubsection[Anchor]{Anchor~\cite{ribeiro2018anchors}}
Anchor maximizes the coverage of a rectangular region
containing the focal point $x$,
expressed as a conjunction of feature predicates (a rule)
as long as the probability of the black-box classifier $f$
outputting $f(x)$ within the region exceeds a given threshold $\tau$
(\cref{fig:anchor}).
It aims to highlight important features
contributing significantly to the output.
For a discrete $m$-dimensional input space $\ispace$,
a trained black-box classifier $f: \ispace \to \{0,1\}$,
an instance $x \in \ispace$
and a distribution $\mathcal{D}$ over the input space,
a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
The predicate $a_i(z)$ evaluates to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
The reliability of the explanation is defined as the ``accuracy'' of the rule,
and the generality of the explanation is defined as the ``coverage'' of the rule.
The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
\begin{align}
  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor-def-prec} \\
  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
\end{align}
where $\mathcal{D}(z|A)$ is the conditional distribution in the region
where the rule $A$ returns true.
$\Prec(A)$ represents the probability that the output of $f$ matches
between the perturbation $z\sim\mathcal{D}(z|A)$ and the focal point $x$,
and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
Anchor maximizes coverage as long as
the accuracy of the rule $A$ exceeds a given threshold $\tau$.
However, \cref{eq:anchor-def-prec} is not directly computable.
Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$,
the accuracy constraint is relaxed as follows:
\begin{equation}
  \label{eq:const-prec}
  P(\Prec(A)\ge\tau)\ge1-\delta.
\end{equation}
Thus, the following optimization problem is solved:
\begin{equation}
  \label{eq:main-problem}
  A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
  {\arg\max}\Cov(A).
\end{equation}

@@

Anchor maximizes the coverage of region $A$
as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
within $A$ exceeds a given threshold $\tau$.
R-LIME, on the other hand, learns a linear classifier $g$
within the rectangular region $A$ and maximizes the coverage of $A$
under lower constraints on the accuracy of $g$.
We modify Anchor's definition of accuracy in \cref{eq:anchor-def-prec}
as follows:
\begin{equation}
  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=g(z)}], \label{eq:def-prec}
\end{equation}
where $G$ is a hypothesis space of possible linear classifiers.
By solving the optimization problem in \cref{eq:main-problem}
under the modified definition of accuracy in \cref{eq:def-prec},
we can select the rule that enables explanation with high accuracy and generality.

\subsection{Algorithm}
{%
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.32\textwidth]{visual-rlime1}
    \includegraphics[width=0.32\textwidth]{visual-rlime2}
    \includegraphics[width=0.32\textwidth]{visual-rlime3}
    \caption[Overview of the R-LIME algorithm]{%
      Overview of the R-LIME algorithm.
      The progression of the algorithm is illustrated from left to right.
      The solid line represents the rectangular region $A$,
      and the dashed line represents the linear approximation model $g$
      learned within $A$.
      The initial value of $A$ is an empty rule (entire input space),
      and predicates are added to $A$, reducing coverage.
      The process continues until $\Prec(A)\ge\tau$ is satisfied,
      at which point the rule with the maximum coverage is output.
    }
  \end{figure}
  \def\myidt{\hspace{\algorithmicindent}}
  \begin{algorithm}[p]
    \small
    \input{src/tex/alg1}
  \end{algorithm}

@@

\subsubsection{Searching Rules with Highest Accuracy}
Given the set of candidate rules $\cands$,
the algorithm selects the $B$ candidate rules with the highest accuracy.
This problem can be formulated
as best arm identification in the multi-armed bandit framework.
Each candidate rule $A_i\in\cands$ is considered as an arm,
and reward of arm $a_i$ follows a Bernoulli distribution
with $P(X=1)=\Prec(A_i)$.
By sampling $z\sim\mathcal{D}(\cdot|A_i)$
and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
To efficiently search the rule (arm) with the highest accuracy,
we employ the KL-LUCB algorithm~\cite{kaufmann2013information}.
The pseudo-code is shown in \cref{alg:best-cands}.
For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
\begin{equation}
  P(\underset{A\in\cands}{\min}\Prec(A)\ge
  \underset{A'\in\mathcal{A}}{\min}\Prec(A')-\epsilon)\ge1-\delta.
\end{equation}
However,
the KL-LUCB algorithm assumes that the reward distribution for each arm
remains unchanged,
while our method updates the classifier $g_i$ with each sampling,
which may not satisfy the assumption.
This issue is discussed further in \cref{sec:reward}.

@@

  {%
    \def\scale{0.315}
    \def\dir{exp1/}
    \def\imgwidth{0.3\textwidth}
    \def\hspacebase{\hspace{-1.5em}}
    \def\vspacebase{\vspace{0.5em}}
    \def\vspacebeforecaption{\vspace{-0.4em}}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \begin{subfigure}[t]{\textwidth}
          \hspace{-10pt}
          \includegraphics[scale=\scale]{exp1/lime-0012}
          \caption{LIME}\label{fig:lime-0}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0012-70}  % chktex 8
          \caption{Anchor ($\tau=0.70$)}\label{fig:anchor-0-70}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0012-90}  % chktex 8
          \caption{Anchor ($\tau=0.90$)}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/rlime-0012-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-17pt}
          \includegraphics[scale=\scale]{exp1/rlime-0012-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance A by LIME and R-LIME]{%
        Explanation for Instance A by LIME and R-LIME\@.
      }\label{fig:A}
    \end{figure}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspace{-26.5pt}
          \includegraphics[scale=\scale]{exp1/lime-0011}
          \caption{LIME}\label{fig:lime-1}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0011-70}  % chktex 8
          \caption{Anchor ($\tau=0.70$)}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0011-90}  % chktex 8
          \caption{Anchor ($\tau=0.90$)}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/rlime-0011-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-20pt}
          \includegraphics[scale=\scale]{exp1/rlime-0011-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance B by LIME and R-LIME]{%
        Explanation for Instance B by LIME and R-LIME\@.
      }\label{fig:B}
    \end{figure}
  }

@@

\begin{figure}[t]
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.36,valign=t]{exp2/box_plot}
    \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
      Comparison of local accuracy between LIME and R-LIME\@.
      R-LIME achieved higher and less variable accuracy compared to LIME\@.
    }\label{fig:box-plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.35,valign=t]{exp2/comp_cov}
    \vspace{3pt}
    \caption[Comparison of Coverage between Anchor and R-LIME]{%
      Comparison of coverage between Anchor and R-LIME\@.
      R-LIME achieved higher coverage compared to Anchor
      for almost values of $\tau$, especially for relatively small $\tau$.
    }\label{fig:coverage}
  \end{subfigure}
  \caption{Comparison of existing methods (LIME, Anchor) and R-LIME.}
\end{figure}

@@

\section{Discussion}
 {%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
 }

@@

A first possible solution to this problem is modifying the loss function.
Using weighted logistic loss or Focal Loss~\cite{lin2020focal}
as the loss function might lead to the generation of more useful explanations
in the case of imbalanced label distribution.
Another solution involves adding constraints
to limit the label distribution bias within the approximation region.
In addition to \cref{eq:const-prec}, adding a constraint like
\begin{equation}
  {%
    \left(
    \mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathbbm{1}_{f(z)=1}]-\frac{1}{2}
    \right)
  }^2<\mu
\end{equation}
could suppress the excessive expansion of the approximation region.

>>>>

% We import package amsmath before the documentclass to avoid the warning.
% Command '\usepackage{amsmath}' results in the following warning:
% ------------------------------
% Package amsmath Warning: Unable to redefine math accent \vec.
% ------------------------------
% cf. https://tex.stackexchange.com/questions/102507/how-to-fix-this-amsmath-warning-about-redefining-vec
\RequirePackage{amsmath} % for environments such as align

@@

@@

\usepackage[export]{adjustbox} % for valign option in \includegraphics
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule

\usepackage{cleveref} % for \cref
\usepackage{csvsimple} % for \csvreader
\usepackage{dsfont} % for \mathds
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

@@

@@

% The authors' affiliations
\institute{Division of Computer Science and Information Technology\\
  Graduate School of Information Sci.\ and Tech.,
  Hokkaido University\\
  Sapporo 060--0814, JAPAN,\\
  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}
}

@@

\section{Introduction}
In recent years,
complex machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvements in accuracy.
However,
their increasing complexity and black-box nature pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the lack of transparency becomes a major obstacle to implementation.
In order to address this problem,
extensive research has focused on post-hoc explanations for complex models
~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
Post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
with the latter further classified into \emph{global} and \emph{local} methods
based on the locality in the input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{src/img/example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{src/img/example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{src/img/example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \vspace{-2.24cm}
    \includegraphics[scale=\scale]{src/img/example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

@@

\section{Proposed Method}
\begin{figure}[tbp]
  \centering
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{src/img/visual-lime}
    \caption{%
      LIME\@: Locally approximates the decision boundary around the focal point.
    }\label{fig:lime}
  \end{subfigure}%
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{src/img/visual-anchor}
    \caption{%
      Anchor: Maximizes coverage of a rectangular region
      containing the focal point under accuracy constraints.
    }\label{fig:anchor}
  \end{subfigure}
  \hspace{0.03\textwidth}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{src/img/visual-rlime3}
    \caption{%
      R-LIME\@:
      Maximizes coverage of a rectangular region
      under lower constraints on the accuracy of the linear classifier.
    }\label{fig:rlime}
  \end{subfigure}
  \caption[Visual comparison of LIME, Anchor and R-LIME]{%
    Visual comparison of LIME, Anchor and R-LIME (our method).
    The dashed line represents the local linear approximation model,
    and the solid line represents the rectangular region containing the focal point.
  }
\end{figure}

@@

\subsubsection[Anchor]{Anchor~\cite{ribeiro2018anchors}}
Anchor maximizes the coverage of a rectangular region
containing the focal point $x$,
expressed as a conjunction of feature predicates (a rule)
as long as the probability of the black-box classifier $f$
outputting $f(x)$ within the region exceeds a given threshold $\tau$
(\cref{fig:anchor}).
It aims to highlight important features
contributing significantly to the output.
For a discrete $m$-dimensional input space $\ispace$,
a trained black-box classifier $f: \ispace \to \{0,1\}$,
an instance $x \in \ispace$
and a distribution $\mathcal{D}$ over the input space,
a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
The predicate $a_i(z)$ evaluates to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
The reliability of the explanation is defined as the ``accuracy'' of the rule,
and the generality of the explanation is defined as the ``coverage'' of the rule.
The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
\begin{align}
  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathds{1}_{f(z)=f(x)}], \label{eq:anchor-def-prec} \\
  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)],
\end{align}
where $\mathcal{D}(z|A)$ is the conditional distribution in the region
where the rule $A$ returns true.
$\Prec(A)$ represents the probability that the output of $f$ matches
between the perturbation $z\sim\mathcal{D}(z|A)$ and the focal point $x$,
and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.
Anchor maximizes coverage as long as
the accuracy of the rule $A$ exceeds a given threshold $\tau$.
However, \cref{eq:anchor-def-prec} is not directly computable.
Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$,
the accuracy constraint is relaxed as follows:
\begin{equation}
  \label{eq:const-prec}
  P(\Prec(A)\ge\tau)\ge1-\delta.
\end{equation}
Thus, the following optimization problem is solved:
\begin{equation}
  \label{eq:main-problem}
  A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
  {\arg\max}\Cov(A).
\end{equation}

@@

Anchor maximizes the coverage of region $A$
as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
within $A$ exceeds a given threshold $\tau$.
R-LIME, on the other hand, learns a linear classifier $g$
within the rectangular region $A$ and maximizes the coverage of $A$
under lower constraints on the accuracy of $g$.
We modify Anchor's definition of accuracy in \cref{eq:anchor-def-prec}
as follows:
\begin{equation}
  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathds{1}_{f(z)=g(z)}], \label{eq:def-prec}
\end{equation}
where $G$ is a hypothesis space of possible linear classifiers.
By solving the optimization problem in \cref{eq:main-problem}
under the modified definition of accuracy in \cref{eq:def-prec},
we can select the rule that enables explanation with high accuracy and generality.

\subsection{Algorithm}
{%
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.32\textwidth]{src/img/visual-rlime1}
    \includegraphics[width=0.32\textwidth]{src/img/visual-rlime2}
    \includegraphics[width=0.32\textwidth]{src/img/visual-rlime3}
    \caption[Overview of the R-LIME algorithm]{%
      Overview of the R-LIME algorithm.
      The progression of the algorithm is illustrated from left to right.
      The solid line represents the rectangular region $A$,
      and the dashed line represents the linear approximation model $g$
      learned within $A$.
      The initial value of $A$ is an empty rule (entire input space),
      and predicates are added to $A$, reducing coverage.
      The process continues until $\Prec(A)\ge\tau$ is satisfied,
      at which point the rule with the maximum coverage is output.
    }
  \end{figure}
  \def\myidt{\hspace{\algorithmicindent}}
  \begin{algorithm}[p]
    \small
    \input{src/tex/alg1}
  \end{algorithm}

@@

\subsubsection{Searching Rules with Highest Accuracy}
Given the set of candidate rules $\cands$,
the algorithm selects the $B$ candidate rules with the highest accuracy.
This problem can be formulated
as best arm identification in the multi-armed bandit framework.
Each candidate rule $A_i\in\cands$ is considered as an arm,
and reward of arm $a_i$ follows a Bernoulli distribution
with $P(X=1)=\Prec(A_i)$.
By sampling $z\sim\mathcal{D}(\cdot|A_i)$
and obtaining the reward $\mathds{1}_{f(z)=g_i(z)}$ for each trial,
the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
To efficiently search the rule (arm) with the highest accuracy,
we employ the KL-LUCB algorithm~\cite{kaufmann2013information}.
The pseudo-code is shown in \cref{alg:best-cands}.
For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
\begin{equation}
  P(\underset{A\in\cands}{\min}\Prec(A)\ge
  \underset{A'\in\mathcal{A}}{\min}\Prec(A')-\epsilon)\ge1-\delta.
\end{equation}
However,
the KL-LUCB algorithm assumes that the reward distribution for each arm
remains unchanged,
while our method updates the classifier $g_i$ with each sampling,
which may not satisfy the assumption.
This issue is discussed further in \cref{sec:reward}.

@@

  {%
    \def\scale{0.315}
    \def\dir{exp1/}
    \def\imgwidth{0.3\textwidth}
    \def\hspacebase{\hspace{-1.5em}}
    \def\vspacebase{\vspace{0.5em}}
    \def\vspacebeforecaption{\vspace{-0.4em}}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \begin{subfigure}[t]{\textwidth}
          \hspace{-10pt}
          \includegraphics[scale=\scale]{src/experiments/exp1/lime-0012}
          \caption{LIME}\label{fig:lime-0}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0012-70}  % chktex 8
          \caption{Anchor ($\tau=0.70$)}\label{fig:anchor-0-70}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0012-90}  % chktex 8
          \caption{Anchor ($\tau=0.90$)}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0012-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-17pt}
          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0012-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance A by LIME and R-LIME]{%
        Explanation for Instance A by LIME and R-LIME\@.
      }\label{fig:A}
    \end{figure}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspace{-26.5pt}
          \includegraphics[scale=\scale]{src/experiments/exp1/lime-0011}
          \caption{LIME}\label{fig:lime-1}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0011-70}  % chktex 8
          \caption{Anchor ($\tau=0.70$)}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{src/experiments/exp1/anchor-0011-90}  % chktex 8
          \caption{Anchor ($\tau=0.90$)}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0011-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-20pt}
          \includegraphics[scale=\scale]{src/experiments/exp1/rlime-0011-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance B by LIME and R-LIME]{%
        Explanation for Instance B by LIME and R-LIME\@.
      }\label{fig:B}
    \end{figure}
  }

@@

\begin{figure}[t]
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.36,valign=t]{src/experiments/exp2/box_plot}
    \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
      Comparison of local accuracy between LIME and R-LIME\@.
      R-LIME achieved higher and less variable accuracy compared to LIME\@.
    }\label{fig:box-plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.35,valign=t]{src/experiments/exp2/comp_cov}
    \vspace{3pt}
    \caption[Comparison of Coverage between Anchor and R-LIME]{%
      Comparison of coverage between Anchor and R-LIME\@.
      R-LIME achieved higher coverage compared to Anchor
      for almost values of $\tau$, especially for relatively small $\tau$.
    }\label{fig:coverage}
  \end{subfigure}
  \caption{Comparison of existing methods (LIME, Anchor) and R-LIME.}
\end{figure}

@@

\section{Discussion}
 {%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{src/img/visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{src/img/visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
 }

@@

A first possible solution to this problem is modifying the loss function.
Using weighted logistic loss or Focal Loss~\cite{lin2020focal}
as the loss function might lead to the generation of more useful explanations
in the case of imbalanced label distribution.
Another solution involves adding constraints
to limit the label distribution bias within the approximation region.
In addition to \cref{eq:const-prec}, adding a constraint like
\begin{equation}
  {%
    \left(
    \mathbb{E}_{z\sim\mathcal{D}(z\mid A)}[\mathds{1}_{f(z)=1}]-\frac{1}{2}
    \right)
  }^2<\mu
\end{equation}
could suppress the excessive expansion of the approximation region.
